Describing demographic models is hard

### 2020-05-19 paper.tex
Minor tweaks.

These errors suggests three lessons. 
First, the msprime API design was poorly designed, 
\dncomment{Still don't like this word. Again if msprime is poor then most bioinformatics 
software is a dumpster fire. What about ``...msprime API can be adapted to 
simplify common use-cases''? A bit clunky but maybe along those lines
}
requiring the user to pass 
three separate parameters to specify a demographic model. 
In \msprime\ 1.0 we introduce
a Demography class, which wraps these three parameters.
Thus, instead of writing
\begin{lstlisting}[frame=single]
dbg = msprime.DemographyDebugger(
  population_configurations=population_configurations,
  migration_matrix=migration_matrix,
  demographic_events=demographic_events)
dbg.print_history()
ts = msprime.simulate(
  population_configurations=population_configurations,
  migration_matrix=migration_matrix,
  demographic_events=demographic_events)
\end{lstlisting}
we would now write
\begin{lstlisting}[frame=single]
dbg = demography.debug()
dbg.print_history()
ts = msprime.simulate(demography=demography)
\end{lstlisting}

Second, testing of the final simulated data is important. This can be challenging, 
because the amount of simulated data can be large. However, recent progress in 
computing summary statistics from tree sequence data can make this easier~\cite{ralph2020efficiently}. 
Even if the entire simulation data cannot be easily evaluated, subsets of the data 
can be examined to identify large error.

@@

Defining demographic models is error prone \dncomment{Just a thought, but alternatively could say 
``Demographic models are complex''}, and incorrect implementation can  
impact downstream analysis and interpretation. The errors that we highlighted here have 
exposed some weaknesses of the current \msprime\ API, which will be fixed in an 
upcoming release. Recognition of these difficulties is also a 
primary motivating factor in efforts to standardize and vet demographic model 
implementation in \stdpopsim~\cite{adrion2019community}, with quality-controlled 
models and simulation resources for a growing number of commonly studied species.

@@

\begin{itemize}
\item Figure 1: plotted using \texttt{demography} package (\url{https://github.com/apragsdale/demography}),
allele frequency spectrum computed using \texttt{moments}~\cite{jouganous2017inferring}, and LD curves
computed using \texttt{moments.LD}~\cite{ragsdale2019models}. $F_{ST}$ and other statistics computed
from the expected AFS.
\item Figure 2: original pipeline from \url{https://github.com/armartin/ancestry_pipeline/blob/master/simulate_prs.py},
reran the experiment, with code available at \url{https://github.com/apragsdale/PRS}
\end{itemize}

>>>>

These errors suggests three lessons.
First, the msprime API design was poorly designed,
\dncomment{Still don't like this word. Again if msprime is poor then most bioinformatics
software is a dumpster fire. What about ``...msprime API can be adapted to
simplify common use-cases''? A bit clunky but maybe along those lines
}
requiring the user to pass
three separate parameters to specify a demographic model.
In \msprime\ 1.0 we introduce
a Demography class, which wraps these three parameters.
Thus, instead of writing
\begin{lstlisting}[frame=single]
dbg = msprime.DemographyDebugger(
  population_configurations=population_configurations,
  migration_matrix=migration_matrix,
  demographic_events=demographic_events)
dbg.print_history()
ts = msprime.simulate(
  population_configurations=population_configurations,
  migration_matrix=migration_matrix,
  demographic_events=demographic_events)
\end{lstlisting}
we would now write
\begin{lstlisting}[frame=single]
demography = msprime.Demography(
  population_configurations=population_configurations,
  migration_matrix=migration_matrix,
  demographic_events=demographic_events)
dbg = demography.debug()
dbg.print_history()
ts = msprime.simulate(demography=demography)
\end{lstlisting}

Second, testing of the final simulated data is important. This can be challenging,
because the amount of simulated data can be large. However, recent progress in
computing summary statistics from tree sequence data can make this
easier~\citep{ralph2020efficiently}.
Even if the entire simulation data cannot be easily evaluated, subsets of the data
can be examined to identify large error.

@@

Defining demographic models is error prone \dncomment{Just a thought, but alternatively could say
``Demographic models are complex''}, and incorrect implementation can
impact downstream analysis and interpretation. The errors that we highlighted here have
exposed some weaknesses of the current \msprime\ API, which will be fixed in an
upcoming release. Recognition of these difficulties is also a
primary motivating factor in efforts to standardize and vet demographic model
implementation in \stdpopsim~\citep{adrion2019community}, with quality-controlled
models and simulation resources for a growing number of commonly studied species.

@@

\begin{itemize}
\item Figure 1: plotted using \texttt{demography} package (\url{https://github.com/apragsdale/demography}),
allele frequency spectrum computed using \texttt{moments}~\citep{jouganous2017inferring}, and LD curves
computed using \texttt{moments.LD}~\citep{ragsdale2019models}. $F_{ST}$ and other statistics computed
from the expected AFS.
\item Figure 2: original pipeline from \url{https://github.com/armartin/ancestry_pipeline/blob/master/simulate_prs.py},
reran the experiment, with code available at \url{https://github.com/apragsdale/PRS}
\end{itemize}
